Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-10-27 Article/main.tex
Added and Updated Final Doc Latex

\begin{itemize}
\item[1.] Literature surrounding the applicable fields was researched
\item[2.] Case studies concerning serious games was studied and similarities noted
\item[3.] Select theories that aid this process were pinpointed
\item[4.] From this research, recommendations for the knowledge domains were made
\end{itemize}

>>>>

\begin{enumerate}

\item Literature surrounding the applicable fields was researched
\item Case studies concerning serious games was studied and similarities noted
\item Select theories that aid this process were pinpointed
\item From this research, recommendations for the knowledge domains were made
\end{enumerate}
